### 2022-06-06 main/chapter_2ljets.tex
add multi contours figure

Figure~\ref{fig:2ljets_summary_no_sr}
Figure~\ref{fig:2ljets_fit_corrmatrix}
Figure~\ref{fig:2ljets_fit_parameters}

@@

>>>>

Figure~\ref{fig:2ljets_summary_no_sr}
Figure~\ref{fig:2ljets_fit_corrmatrix}
Figure~\ref{fig:2ljets_fit_parameters}
Figure~\ref{fig:2ljets_fit_muti_contourss}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although figures were produced before unblinding, with older samples and region
designs, the general message has not changed.
Values of CLs from mean data in the combined fit are are overlaid on the grid.
}
\label{fig:2ljets_fit_muti_contourss}
\end{figure}
